---
title: "Data 607 Assignment 09"
author: "Jun Pan"
date: "October 27, 2018"
output: html_document
---


Assignment - Web APIs 

The New York Times web site provides a rich set of APIs, as described here:  http://developer.nytimes.com/docs You'll need to start by signing up for an API key. Your task is to choose one of the New York Times APIs, construct an interface in R to read in the JSON data, and transform it to an R dataframe. 

set working enviornment
```{r}
if (!require('dplyr')) install.packages('dplyr')
if (!require('stringr')) install.packages('stringr')
if (!require('RJSONIO')) install.packages('RJSONIO')
```

Sources: http://developer.nytimes.com/

Key:
```{r}
key <- "8ba80c2191ec4062aa14565fb5adab43"   #API Key
```




GET
Get call to the API endpoint and get the feed
```{r}
# add url and text required for call
url <- "https://developer.nytimes.com/most_popular_api_v2.json"
df <- paste0(url, "?")

# make call
feed <- fromJSON(paste0(df, handler = NULL, default.size=200, depth=350,allowComments=TRUE, key))
```

make a datafram
```{r}
sub <- feed$results
sub$pub_date <- unlist(str_extract(sub$published_date, ".+?(?=T)"))
sub$pub_time <- unlist(str_extract(sub$published_date, "(?<=T)(.*)"))

sub <- sub %>% 
    filter(section == "Movies") %>% 
    select(title, abstract, byline, url, pub_date, pub_time)
```

API scrabed data
```{r}
knitr::kable(sub)
```

```{r}
class(sub)
```

```{r}
head(sub)
```

```{r}
sub
```


